Volatility Metric to Detect Anomalies in Source Code Repositories

### 2021-09-18 paper/article.tex
sent to bcnc

\documentclass[sigplan,10pt,nonacm=true]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}

\title{Volatility Metric to Detect Anomalies in Source Code Repositories}
\author{Yegor Bugayenko}{}{}
\email{yegor256@gmail.com}
\affiliation{\institution{}\city{Moscow}\country{Russia}}
\ccsdesc[100]{Software and its engineering~Metrics}
\keywords{Metrics, Software Size, Software Maintainability}
% \setcopyright{acmcopyright}
% \copyrightyear{2020}
% \acmYear{2020}

@@

% The source code of Ruby and Python scripts used to do the research
% is available in GitHub repository \texttt{yegor256/volatility-vs-size}.

\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

>>>>

\documentclass[sigplan,10pt,screen]{acmart}
% \settopmatter{printfolios=false,printccs=false,printacmref=false}

\title{Volatility Metric to Detect Anomalies in Source Code Repositories}
\author{Yegor Bugayenko}
\orcid{0000-0001-6370-0678}
\email{yegor256@gmail.com}
\affiliation{\institution{}\city{Moscow}\country{Russia}}

\setcopyright{acmcopyright}
\acmPrice{15.00}
\acmDOI{10.1145/3486949.3486961}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{splashws21bcncmain-p41-p}
\acmISBN{978-1-4503-9125-2/21/10}
\acmConference[BCNC '21]{Proceedings of the 1st ACM SIGPLAN International Workshop on Beyond Code: No Code}{October 17, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 1st ACM SIGPLAN International Workshop on Beyond Code: No Code (BCNC '21), October 17, 2021, Chicago, IL, USA}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011074.10011111.10011696</concept_id>
<concept_desc>Software and its engineering~Maintaining software</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Software and its engineering~Maintaining software}
\keywords{Metrics, Software Size, Software Maintainability}

@@

The source code of Ruby and Python scripts used to do the research
is available in GitHub repository:\newline\texttt{yegor256/volatility-vs-size}.

\bibliographystyle{ACM-Reference-Format}
\bibliography{main}
\clearpage
